Study of Intra- and Inter-Job Interference with Different Job allocations

### 2015-10-15 submission.tex
cut the abstraction short

Network contention between concurrently running jobs on HPC system is one of the primary causes of performance variability. Optimizing job allocation and avoiding network sharing are proven techniques to alleviate network contention and performance degradation. In this work, we propose a novel job communication pattern aware allocation strategy which serves as a critical module in our future HPC batch scheduler. The novelty of our new strategy is that it makes allocation decisions based on job’s communication pattern in addition to system topology and resource availability information. The scheduler uses job communication patterns information to decide whether its performance relies heavily on the network or not, and what the potential intra- and inter-job interference would be for a given allocation. Thus, the scheduler can pick a preferable resource allocation based on a specific job's communication pattern. We validate the effectiveness of our new design using traces collected from three representative parallel applications. The idea presented in this paper is widely applicable: HPC parallel applications have common communication patterns, and allocating resource with communication pattern awareness can improve performance on these systems with a variety of network topologies.

>>>>

Network contention between concurrently running jobs on HPC system is one of the primary causes of performance variability. Optimizing job allocation and avoiding network sharing are proven techniques to alleviate network contention and performance degradation. In this work, we choose three representative HPC applications from DOE Design Forward Project and conduct detailed analysis about intra- and inter-job interference with them. By scrutinizing the communication behaviors of these applications, we identify the relation between applications' communication pattern and the possible interference when they running with different allocations. We propose a novel and flexible strategy that makes allocation with awareness of job's communication pattern. The new strategy can effectively alleviate the performance degradation caused by interference.
